On Secure Delegation of SampBQP with a Classical Client

### 2020-01-23 blind.tex
Write first draft for blind delegation proof

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{itemize}

@@

\begin{algorithm}
	\caption{Verifiable, secure, and constant round delegation}
	\label{ProtoPrivateDelegation}
	\begin{algorithmic}[1]
		\Procedure{Delegation}{C, x}
			\State Compute $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
			\State Get $y$ from the server
			\State \Return $\mathsf{QHE.Dec}(y)$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{thm}
    \label{QPIP1thm}
	\protoref{ProtoPrivateDelegation} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
\end{thm}
\begin{proof}
	The client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$. \Ethan{Errors terms?}

	Which by the properties of homomoprhic encryption should decode to $\rho$ that is $\varepsilon$-indistinguishable to $C(x)$ \Ethan{Fill in error terms}

	As decoding commutes with measurements, the verifier requests its desired measurements of $\rho$ and decode it.
\end{proof}

\begin{thm}
	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
\end{thm}
\begin{proof}
	The verifier's first message is encrypted into $\tilde{x}$ in an IND-CPA way as a ciphertext.
	The verifier's second message is the basis choice of Hadamard or test rounds, which can be done using public coins.

>>>>

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
\end{itemize}

Furthermore, one could either decode or measure first, in the following sense:
\begin{lemma}
	\label{decodeMeasureOrder}
	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{lemma}

@@

\begin{algorithm}
	\caption{Verifiable, secure, and constant round delegation}
	\label{ProtoPriv}
	\begin{algorithmic}[1]
		\Procedure{Delegation}{C, x}
			\State Compute $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{QHE.Eval}_{evk}(C, \tilde{x})$
			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
			\State Request $\Lambda'$ based on \autoref{decodeMeasureOrder}, where $\Lambda$ is the basis choice if $C(x)$ were delegated.
			\State Let $y$ be the measurement results from the server
			\State \Return $\widehat{\mathsf{QHE.Dec}_{sk}}(y)$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{thm}
    \label{QPIP1thm}
	\myprotoref{ProtoPriv} can evaluate any $L\in\SampBQP$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$.
\end{thm}
\begin{proof}
	Suppose $\bbV$ accepts $\bbP'$ at least $\delta$ of the time.

	Then the $\QPIP_0$ delegation must accept at least that often too,
	so the client will receive a sample from $\mathsf{Eval}_{evk}(C, \tilde{x})$ with at most inverse poly error. \Ethan{security param?}

	The verifier ends up with a state within inverse poly distance to
		$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'(\tilde{C}(\tilde{x}))$$
		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\tilde{C}(\tilde{x}))$$
		$$=\Lambda\circ\mathsf{QHE.Dec}_{sk}(\mathsf{QHE.Eval}_{evk}(C, \tilde{x}))$$

	By the properties of homomoprhic encryption, with overwhelming probability this is indistinguishable to \Ethan{Check if it's true} $\Lambda(C(x))$
\end{proof}

\begin{thm}
	\myprotoref{ProtoPriv} is IND-CPA secure.
\end{thm}
\begin{proof}
	The verifier's first message is encrypted into $\tilde{x}$ in an IND-CPA way as a ciphertext.
	The verifier's second message is the basis choice of Hadamard or test rounds, which can be done using public coins.
